%% This defines the bibliography file (main.bib) and the bibliography style.
%% If you want to create a bibliography file by hand, change the contents of
%% this file to a `thebibliography' environment.  For more information 
%% see section 4.3 of the LaTeX manual.
{\fontencoding{T1}\fontseries{bx}\fontshape{n} \fontsize{0,9cm}{5em}\selectfont
Bibliography\\
}
\begin{singlespace}
\bibliography{main}
\bibliographystyle{plain}

[1]Nvidia, “Kepler GK110, The Fastest, Most Efficient HPC Architecture Ever Built” [Whitepaper]. http://www.nvidia.com/content/PDF/kepler/NVIDIA-Kepler-GK110-Architecture-Whitepaper.pdf\\

[2]Christos D. Antonopoulos, “High performance computing” [Lecture Notes], University of Thessaly, 2013. http://inf-server.inf.uth.gr/courses/CE421/lectures.php\\

[3]Nvidia, “CUDA Programming Model Overview”. http://moss.csc.ncsu.edu/~mueller/cluster/nvidia/GPU+CUDA.pdf \\

[4]Nvidia, “CUDA C Programming Guide”. http://docs.nvidia.com/cuda/cuda-c-programming-guide/index.html\\

[5]T. Brandvik and G. Pullan . "SBLOCK: a framework for efficient Stencil-Based PDE solvers on multi-core platforms", In Computer and Information Technology (CIT), 2010 IEEE 10th International Conference on, page 1181–1188, 2010\\

[6]P. Micikevicius. 2009. "3d Finite difference computation on GPUs using CUDA," GPGPU-2: Proceedings of 2nd Workshop on General Purpose Processing on Graphics Processing Units (New York, NY, USA), ACM, 2009\\

[7]David L. Foster. 2011,"GPU Acceleration of Solving Parabolic Partial Differential Equations Using Difference Equations": Proceedings of the 2011 International Conference on Parallel and Distributed Processing Techniques and Applications, 2011\\

[8]S. Williams, J. Shalf, L. Oliker, S. Kamil , P. Husbands, and K. Yelick, “Scientific Computing Kernels on the Cell Processor,” Int. J. Parallel Program., vol. 35, no. 3, pp. 63–298, 2007\\

[9]Schäfer, Andreas and Fey, Dietmar. (2011) "High Performance Stencil Code Algorithms for GPGPUs": Proceedings of the International Conference on Computational Science, ICCS 2011\\

[10]D.P. Playne and K.A. Hawick. (2010) "Hierarchical and Multi-level Schemes for Finite Difference Methods on GPUs ": Technical Note, Computer Science, Massey University\\

[11]Daniel Egloff, GPUs in Financial Computing Part I: High-Performance Tridiagonal Solvers on GPUs. Wilmott Magazine, September 1, 2010\\

[12]Daniel Egloff, GPUs in financial computing part III: ADI solvers on GPUs with application to stochastic volatility, Wilmott Magazine, March 2011\\

[13]Won-Ki Jeong, Ross Whitaker, Mark Dobin. (2006) “Interactive 3D Seismic Fault Detection on the Graphics Hardware.”: Proceedings of International Workshop on Volume Graphics 2006, pp.111-118\\

[14]Hee-Seok Kim, Shengzhao Wu, Li-wen Chang and Wen-mei W. Hwu “A Scalable Tridiagonal Solver for GPUs” Electrical and Computer Engineering ,University of Illinois at Urbana-Champaign\\ 

[15]R. S. Oliveira, B. M. Rocha, R. M. Amorim et al., “Comparing Cuda, OpenCL and Opengl implementations of the cardiac monodomain equations,” in Parallel Processing and Applied Mathematics, R. Wyrzykowski, J. Dongarra, K. Karczewski, and J. Wasniewski, Eds., vol. 7204 of Lecture Notes in Computer Science, pp. 111–120, Springer, Berlin, Germany, 2012\\

[16]Jens Kruger and Rudiger Westermann, “Linear Algebra Operators for GPU Implementation of Numerical Algorithms” International Conf. on Computer Graphics and Interactive Techniques, 2005\\

[17]Daisuke Sato , Yuanfang Xie , James N. Weiss ,Zhilin Qu ,Alan Garfinkel, Allen R. Sanderson ,"Acceleration of cardiac tissue simulation with graphic processing units", 2009\\

[18]Andrés Mena and Jose F Rodriguez, "Using Graphic Processor Units for the Study of Electric Propagation in Realistic Heart Models", Computing in Cardiology (CinC) Publication Year: 2012, Page(s): 37 - 40\\

[19]Li-Wen Chang, John A. Stratton, Hee-Seok Kim, and Wen-Mei W. Hwu ,"A Scalable, Numerically Stable, High-performance Tridiagonal Solver using GPUs", University of Illinois at Urbana-Champaign\\

[20]Abhijeet Gaikwad and Ioane Muni Toke, " Parallel Iterative Linear Solvers on GPU: A Financial Engineering Case " , In proceeding of: Proceedings of the 18th Euromicro Conference on Parallel, Distributed and Network-based Processing, PDP 2010, Pisa, Italy, February 17-19, 2010\\

[21]Section of Scientific Computing ,Department of Informatics and Mathematical Modeling, Technical University of Denmark ,"GPULab Library - a High-Performance Library for PDE Solvers"\\

[22]Jeff Bolz, Ian Farmer, Eitan Grinspun ,Peter Schröder," Sparse Matrix Solvers on the GPU: Conjugate Gradients and Multigrid"\\

[23]Dominik Göddeke, Robert Strzodka: “Cyclic Reduction Tridiagonal Solvers on GPUs Applied to Mixed-Precision Multigrid”.  IEEE Trans. Parallel Distrib. Syst. 22(1): 22-32 (2011)\\

[24]Y. Zhang, J. Cohen, and J. D. Owens, “Fast tridiagonal solvers on the GPU,” in Proceedings of the 15th ACM SIGPLAN Symposium on Principles and Practice of Parallel Programming (PPoPP 2010), Jan. 2010, pp. 127–136\\

[25]D. Egloff, “High performance ﬁnite difference PDE solvers on GPUs.” 
Available at: http://download.quantalea.net/fdm gpu.pdf, Feb. 2010\\

[26]R. W. Hockney, A fast direct solution of Poisson’s equation using Fourier analysis, J. ACM, 12 (1965)\\

\bibliographystyle{plain}
\end{singlespace}
